Productivity estimation in waterfowl using a non-invasive method

### 2021-09-07 Code/Draft_ruddy_duck_productivity.Rmd
abstract modif
biblio path

---
lang: en-EN
bibliography: ../../../../Biblio/JabRef/Library_OFB/Library_OFB.bib
csl: ../../../../Biblio/JabRef/Library_OFB/Styles/ecology.csl
title: "Productivity estimation in waterfowl using a non-invasive method"
author: 
- Adrien Tableau^[Office Français de la Biodiversité, France - adrien.tableau@ofb.gouv.fr - contribution in data analyses & writing]
- Alain Caizergues^[Office Français de la Biodiversité, France - alain.caizergues@ofb.gouv.fr - contribution in writing]
- Iain Henderson^[Animal and Plant Health Agency, United Kingdom - iain.henderson@apha.gov.uk - contribution in data collection]
- Sébastien Reeber^[Société Nationale pour la Protection de la Nature, France - sebastien.reeber@snpn.fr - contribution in data collection]
- Matthieu Guillemain^[Office Français de la Biodiversité, France -  matthieu.guillemain@ofb.gouv.fr - contribution in writing]

@@

The response of a waterfowl population to a harvest pressure depends on its capacity to renew. The recruitment, i.e. the number of young adults reproducing for the first time, is a key indicator to describe the renewal of a population, and therefore an essential tool in population management. The productivity, i.e. the number of recruits per breeder, is even more informative because it is independent of the population size and allows a comparison over time and between species. The proportion of young adults in a waterfowl population is often estimated from game-hunting samples. However, this proportion, which is a main step in estimating productivity, is not accessible in years without harvest, or with a low harvest rate. Moreover, the age-structure in the harvest samples, commonly called hunting bag, does not necessarily reflect the underlying age-structure of the population. It is often skewed towards juveniles and can lead to an overestimation of the productivity. In waterfowl, adult males usually display brighter colours than juveniles and females. This dichromatism can be characterized and monitored from count surveys, a non-invasive method. Such information can be used to infer the proportion of recruits, and consequently the productivity. In using two populations of ruddy duck, *Oxyura oxyura*, this study develops a Bayesian method to estimate the productivity from count data. To judge the accuracy of this approach, the results are compared to productivity estimates from samples. The adult survival can be estimated from both the counting and the sampling methods and is commonly found in the literature. The consistency of the two approaches is thus discussed by comparing the survival estimates with the literature values.

>>>>

---
lang: en-EN
bibliography: ../../../Dropbox/Biblio/Library_OFB.bib
csl: ../../../Dropbox/Biblio/Styles/ecology.csl
title: "Productivity estimation in waterfowl using a non-invasive method"
author: 
- Adrien Tableau^[Office Français de la Biodiversité, France - adrien.tableau@ofb.gouv.fr - contribution in data analyses & writing]
- Alain Caizergues^[Office Français de la Biodiversité, France - alain.caizergues@ofb.gouv.fr - contribution in writing]
- Iain Henderson^[Animal and Plant Health Agency, United Kingdom - iain.henderson@apha.gov.uk - contribution in data collection]
- Sébastien Reeber^[Société Nationale pour la Protection de la Nature, France - sebastien.reeber@snpn.fr - contribution in data collection]
- Matthieu Guillemain^[Office Français de la Biodiversité, France -  matthieu.guillemain@ofb.gouv.fr - contribution in writing]

@@

The response of a waterfowl population to a harvest pressure depends on its capacity to renew. The recruitment, i.e. the number of young adults reproducing for the first time, is a key indicator to describe the renewal of a population, and therefore an essential tool in population management. The productivity, i.e. the number of recruits per breeder, is even more informative because it is independent of the population size and allows a comparison over time and between species. The proportion of young adults in a waterfowl population is often estimated from game-hunting samples. However, this proportion, which is a main step in estimating productivity, is not accessible in years without harvest, or with a low harvest rate. Moreover, the age-structure in the harvest samples, commonly called hunting bag, does not necessarily reflect the underlying age-structure of the population. It is often skewed towards juveniles and can lead to an overestimation of the productivity. In waterfowl, adult males usually display brighter colours than juveniles and females. This dichromatism can be characterized and monitored from count surveys, a non-invasive method. Such information can be used to infer the proportion of young adults, and consequently the productivity. In using two populations of ruddy duck, *Oxyura oxyura*, this study develops a Bayesian method to estimate the productivity from count data. To judge the accuracy of this approach, the results are compared to productivity estimates from samples. The adult survival can be estimated from both the counting and the sampling methods and is commonly found in the literature. The consistency of the two approaches is thus discussed by comparing the survival estimates with the literature values.
